Roster Review (Generic)

### 2019-06-06 rosterReview_generic.Rmd
New projections, found some duplicates, trying some per-team average views

```

@@

rosters_by_position %>% 
  full_join(pos_median_zar) %>% 
  mutate(pos_zar = zar - median_zar) -> rosters_by_position

@@

```

>>>>

#TODO review duplicates
```

@@

rosters_by_position %>% 
  full_join(pos_median_zar) %>% 
  #FIXME two decimal places for pos_zar
  mutate(pos_zar = zar - median_zar) -> rosters_by_position

@@

# Averaging pos_zar by position, overall
# Does this actually indicate good/bad teams?
rosters_by_position %>% 
  filter(team != "Free Agent") %>% 
  group_by(team, position) %>% 
  summarize(avg_pos_zar = mean(pos_zar)) -> team_pos_avg_zar

team_pos_avg_zar %>%  
  ggplot(aes(position, avg_pos_zar, color = position)) +
  geom_point() +
  facet_wrap(~ team) -> team_avg_pos

ggplotly(team_avg_pos)

team_pos_avg_zar %>% 
  ungroup() %>% 
  group_by(team) %>% 
  summarize(avg_pos_zar = mean(avg_pos_zar)) %>% 
  arrange(avg_pos_zar %>% desc)
```
